\textbf{Manual Coding Handbook} \\[1cm] A New Indicator of Automation \\ Based on Patent Text Search

### 2015-06-09 manual_classification/manual_coding_handbook.tex
Make automatic contingency table of classifications
..

\definecolor{mygrey}{rgb}{0.85,0.85,0.85} % make grey for the table
\definecolor{myred}{rgb}{0.85,0.1,0.1} % make grey for the table
\definecolor{mytextgrey}{rgb}{0.25, 0.25, 0.25} % make grey for text
% --------------------------------------------------------

@@

@@

\begin{frame}\frametitle{Practical issues}
	\begin{itemize}	
	\item We will give you an Excel document containing a list of patent numbers such as: 7091471 or 7124853 or 9027105.
	\item Please go to one of the following websites: \\[0.1cm]
 \href{https://www.google.com/patents}{\texttt{https://www.google.com/patents}}\\[0.1cm]
\href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{http://patft.uspto.gov/netahtml/PTO/search-bool.html}}\\[0.1cm]
	and enter the patent number
	\item We recommend using Google Patents first, as it has the nicer interface. If you cannot find it (this happens rarely) or if the patent grant text looks incomplete (also rare), please try at the USPTO search interface.
	\item The right patent might not be the first one in the list. In Google Patents, you might find patents from other countries. You identify the right patent as the one starting with ``US". In the USPTO search interface, the right patent is often the last one in the list (don't ask us why...).
	\end{itemize}
\end{frame}

>>>>

\definecolor{mygrey}{rgb}{0.85,0.85,0.85}
\definecolor{myred}{rgb}{0.85,0.1,0.1}
\definecolor{mytextgrey}{rgb}{0.25, 0.25, 0.25}
\definecolor{mytextyellow}{rgb}{1, 1, 0.9}
% --------------------------------------------------------

@@

\begin{frame}\frametitle{Tradeoffs}
\vspace{0.6cm}
	\begin{itemize}	
	\item Tool vs. automat
	\item Part of larger process vs. independent device
	\item Highly abstract vs. an application to automation is apparent
	\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Practical issues}
	\begin{itemize}	
	\item We will give you an Excel document containing a list of patent numbers such as: 7091471 or 7124853 or 9027105.
	\item Please go to one of the following websites: \\[0.1cm]
 \href{https://www.google.com/patents}{\texttt{\textcolor{myred}{https://www.google.com/patents}}}\\[0.1cm]
\href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{\textcolor{myred}{http://patft.uspto.gov/netahtml/PTO/search-bool.html}}}\\[0.1cm]
	and enter the patent number
	\item We recommend using Google Patents first, as it has the nicer interface. If you cannot find it (this happens rarely) or if the patent grant text looks incomplete (also rare), please try at the USPTO search interface.
	\item The right patent might not be the first one in the list. In Google Patents, you might find patents from other countries. You identify the right patent as the one starting with ``US". In the USPTO search interface, the right patent is often the last one in the list (don't ask us why...).
	\end{itemize}
\end{frame}
